Probabilities of polar alignment in circumbinary disks

### 2024-12-17 src/tex/ms.tex
Mention fpol max at jcr
Remove unneeded discussion about tevol

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/fpol_j.pdf}
    \caption{
        Polar disk fraction $f_\text{polar}$ as a function of $j$ for various distributions $p_{e_\text{b}}(e_\text{b})$. All cases assume isotropic distributions of initial angular momentum. In the thermal case, $p_{e_\text{b}}(e_\text{b}) \propto e_\text{b}$. In the uniform case, $p_{e_\text{b}}(e_\text{b}) = \text{const}$. The case labeled $e_\text{b} < 0.1$ uses a uniform distribution, but restricts the domain to $e_\text{b} \in [0,0.1)$. These three distributions are shown in the inset. The dashed line cases fix $e_\text{b}$ at a particular value.
    }
    \script{f_p_of_j.py}
    \label{fig:fpol_j}
\end{figure*}

@@

\subsection{Timescales}
In order to map a dynamical state to a final alignment (e.g. libration $\mapsto$ polar), we are required to assume that the disk lifetime $t_\text{disk}$ is longer than the disk evolution timescale $t_\text{evol}$. The evolution timescale is the characteristic decay time for a disk whose inclination has been perturbed from a stable point (e.g., polar or coplanar), and while it is described by \citet{lubow2018} in their equation (29), it is only known up to a constant of proportionality:
\begin{equation}
    \label{eq:tevol}
    t_\text{evol} \propto \frac{h^2}{\alpha f^2(1-f)^2 e_\text{b}^2(1+4e_\text{b}^2) \Omega_\text{b}} ,
\end{equation}
where $h\equiv H/r$ is the disk aspect ratio, $f\equiv M_2/M$ is the mass ratio, and $\Omega_\text{b}$ is the binary orbital frequency. The effect of eccentricity is
\begin{equation}
    t_\text{evol} \propto e_\text{b}^{-4}
\end{equation}
when $e_\text{b}$ is small. This suggests that near-circular binaries are much more likely to host misaligned disks that are neither polar nor coplanar. In fact, if it is common for planets to transit eclipsing circular binary systems, then 1) the constant of proportionality in equation (\ref{eq:tevol}) must be very small, or 2) there must be a strong preference for coplanar formation of the disk, or 3) there must be a tendency for circularization of the binary on a longer timescale than $t_\text{evol}$. To date, all known circumbinary planets orbit systems with $a_\text{b} < 1\text{AU}$, some with low eccentricity ($e_\text{b}<0.1$) \TJ{(Cite original papers as well as look at table 1 of \citet{martin2021})}. The low separation of the host binaries is likely a selection effect, as short period transits are much more likely to be detected. \TJ{(Say something else.)}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/fpol_j.pdf}
    \caption{
        Polar disk fraction $f_\text{polar}$ as a function of $j$ for various distributions $p_{e_\text{b}}(e_\text{b})$. All cases assume isotropic distributions of initial angular momentum. In the thermal case, $p_{e_\text{b}}(e_\text{b}) \propto e_\text{b}$. In the uniform case, $p_{e_\text{b}}(e_\text{b}) = \text{const}$. The case labeled $e_\text{b} < 0.1$ uses a uniform distribution, but restricts the domain to $e_\text{b} \in [0,0.1)$. These three distributions are shown in the inset. The dashed line cases fix $e_\text{b}$ at a particular value. Notice the maximum that occurs at $j\approx 0.5$. This occurs because the appearance of crescent orbits along with the disappearance of retrograde orbits at $j=j_\text{cr}$ \citep[eq. A3]{martin2019} make the parameter space that eventually evolves to polar very large.
    }
    \script{f_p_of_j.py}
    \label{fig:fpol_j}
\end{figure*}

@@

\subsection{Timescales}
In order to map a dynamical state to a final alignment (e.g. libration $\mapsto$ polar), we are required to assume that the disk lifetime $t_\text{disk}$ is longer than the disk evolution timescale $t_\text{evol}$. The evolution timescale is the characteristic decay time for a disk whose inclination has been perturbed from a stable point (e.g., polar or coplanar), and while it is described by \citet{lubow2018} in their equation (29), it is only known up to a constant of proportionality:
\begin{equation}
    \label{eq:tevol}
    t_\text{evol} \propto \frac{h^2}{\alpha f^2(1-f)^2 e_\text{b}^2(1+4e_\text{b}^2) \Omega_\text{b}} ,
\end{equation}
where $h\equiv H/r$ is the disk aspect ratio, $f\equiv M_2/M$ is the mass ratio, and $\Omega_\text{b}$ is the binary orbital frequency.
